Abstract

### 2025-10-07 output/Main_text.Rmd
Use latent trait for space transform formulation
It is used later on for expressing the contour plot transformation

\begin{equation}
  `r DISCR_COORDS_TRANSF_EQ`                  (\#eq:trait-coords-orth-spaces-eq)
\end{equation}

for any point, $`r TRAIT_VECTOR`$ or $`r DISCR_VECTOR`$.
This allows representing the coordinates of the discrimination vectors
in the latent space and, conversely,
the coordinates of the latent trait vectors in the test space:
By \@ref(eq:change-basis), \@ref(eq:discr-vector-std),
and  \@ref(eq:trait-coords-orth-spaces-eq)
any coordinate vector $`r DISCR_COORDS`$ in $`r TEST_SPACE_BASIS`$
can be expressed in
$`r LS_BASIS`$ as $`r DISCR_COORDS_TS_EQ`$, and vice versa.
As we can see, the invariance of the model holds,
regardless of the space in which we represent the coordinates.

>>>>

\begin{equation}
  `r TRAIT_COORDS_ORTH_EQ`                    (\#eq:trait-coords-orth-spaces-eq)
\end{equation}

for any point, $`r TRAIT_VECTOR`$ or $`r DISCR_VECTOR`$.
This allows representing the coordinates of the latent space vectors
in the test space and, conversely,
the coordinates of the discrimination vectors in the latent space:
By \@ref(eq:change-basis), \@ref(eq:discr-vector-std),
and  \@ref(eq:trait-coords-orth-spaces-eq)
any coordinate vector $`r TRAIT_COORDS`$ in $`r LS_BASIS`$
can be expressed in $`r TEST_SPACE_BASIS`$ as

\begin{equation}
  `r TRAIT_COORDS_TS_EQ`,                   (\#eq:trait-coords-spaces-transform)
\end{equation}

and vice versa.
As we can see, the invariance of the model holds,
regardless of the space in which we represent the coordinates.
